### 2021-04-05 papers/SYRCoSE/overview.tex
SYRCoSE: WIP --- related work

We also favor the computational encoding of semantics. 
In the line of the recent related works on mechanization 
of operational semantics~\cite{Xia-al:POPL2019, Letan-al:CPP2020, Affeldt-al:ICMPC2019}, 
we encode the semantics as monadic interpreters.  
This allows us to extract~\cite{Letouzey:CCE2008} 
the semantics as a functional program and run it. 
We believe that the possibility to run the semantics 
is a very useful feature, as it allows 
to debug the formal semantics
and helps to develop better intuition about it.

>>>>

We also favor the computational encoding of semantics. 
Similarly to the recent related works on mechanization 
of operational semantics~\cite{Xia-al:POPL2019, Letan-al:CPP2020, Affeldt-al:ICMPC2019}, 
we encode the semantics as monadic interpreters.  
This allows us to extract~\cite{Letouzey:CCE2008} 
the semantics as a functional program and run it. 
We believe that the possibility to run the semantics 
is a very useful feature, as it allows 
to debug the formal semantics
and helps to develop better intuition about it.
